Meta-analysis

### 2019-08-07 05_MetaAnalysis.Rmd
updated lmer analysis from changes stdev calculation

# grain yeild is a significant predictor for yeild error (t value = -2.757)
# does log transformation improve the model

@@

@@

# plot of the mixed effect model, Black line shows the mean lmer regression line
ggplot(PM_MB_train)+
   geom_point(aes(y = Yield_error, x = `grain_yield.t.ha.`, colour = Trial_ref))+
   geom_abline(intercept = c(InterC,lmer.coef$Trial_ref[,1]), 
               slope = c(paramA,lmer.coef$Trial_ref[,2]),
               size = 1.5,
               colour = c("Black",hue_pal()(5)))
   coord_cartesian(xlim = c(0.8, 1.2))

@@

anova(PM_MB_trianLMER,PM_MB_trianLMERx) # random slope model significantly better # P = 0.00378

@@

# plot of the mixed effect model, Black line shows the mean lmer regression line
ggplot(PM_MB_train)+
   geom_point(aes(y = Yield_error, x = `grain_yield.t.ha.`, colour = Trial_ref))+
   geom_abline(intercept = lmer.coefx$Trial_ref[,2], 
               slope = lmer.coefx$Trial_ref[,1],
               size = 1.5,
               colour = hue_pal()(5))+
   coord_cartesian(xlim = c(0, 3))

>>>>

# grain yeild is not a significant predictor for yeild error (t value = -1.613)
#  And the variance decreases as the mean increases, counter to expectation
# does log transformation improve the model

@@

PM_MB_trianLMER.3 <- lmer(log(Yield_error) ~ log(`grain_yield.t.ha.`)+ 
         (1|Trial_ref), data = PM_MB_train)
summary(PM_MB_trianLMER.3) # log(grain yeild) is a significant predictor of log(yeild error)
anova(PM_MB_trianLMER, PM_MB_trianLMER.3) # no significant difference between the models

@@

# plot of the mixed effect model, Black line shows the mean lmer regression line
ggplot(PM_MB_train)+
   geom_point(aes(y = Yield_error, x = `grain_yield.t.ha.`, colour = Trial_ref))+
   geom_abline(intercept = c(InterC,lmer.coef$Trial_ref[,1]), 
               slope = c(paramA,lmer.coef$Trial_ref[,2]),
               size = 1,
               colour = c("Black",hue_pal()(6)))
   coord_cartesian(xlim = c(0.8, 1.2))

@@

anova(PM_MB_trianLMER,PM_MB_trianLMERx) # random slope model NOT significantly better # P = 0.6677

@@

# plot of the mixed effect model, Black line shows the mean lmer regression line
ggplot(PM_MB_train)+
   geom_point(aes(y = Yield_error, x = `grain_yield.t.ha.`, colour = Trial_ref))+
   geom_abline(intercept = lmer.coefx$Trial_ref[,2], 
               slope = lmer.coefx$Trial_ref[,1],
               size = 1.5,
               colour = hue_pal()(6))+
   coord_cartesian(xlim = c(0, 3))
